Abstract Spatial Specification of Stencil Computations

### 2016-06-23 paper.tex
typo

\begin{definition}[Base induction variable]
  An variable \textit{v} of integer type is a \emph{base induction
    variable} if it is the control variable of a ``for''
  loop\footnote{Or equivalent for the target language, \eg{},
    \texttt{do} in Fortan for our implementation}, incremented by $1$ per
iteration. The variable is marked as a base induction variable
only within the scope of the loop, and such variables will be ranged
over by $i$, $j$, $k$. Since we do not use non-base induction
variables (which are traditionally affine transformations of induction
variables) we often simply say \emph{induction variable}. 
\end{definition}

>>>>

\begin{definition}[Base induction variable]
  A variable \textit{v} of integer type is a \emph{base induction
    variable} if it is the control variable of a ``for''
  loop\footnote{Or equivalent for the target language, \eg{},
    \texttt{do} in Fortan for our implementation}, incremented by $1$ per
iteration. The variable is marked as a base induction variable
only within the scope of the loop, and such variables will be ranged
over by $i$, $j$, $k$. Since we do not use non-base induction
variables (which are traditionally affine transformations of induction
variables) we often simply say \emph{induction variable}. 
\end{definition}
